A Component-Based Sensor Network for \\ Environmental Monitoring

### 2009-03-12 docs/icccn2009/paper.tex
Adding the Remote Communication section. It must be finished up...
git-svn-id: svn://localhost/netbeams/trunk@368 559edde2-a4d4-44e0-96fc-4035e40d7396

\begin{table}
\caption{\label{tab:RS232_Config}RS232 Serial Port Configuration}
\centering
\begin{tabular}{l l}
\hline
Baud Rate&9600\\
Data Bit&8\\
Parity&None\\
Handshake&None\\
\hline
\end{tabular}
\end{table}

@@

The YSI Sonde component will pass any messages it generates to the
local DSP. Via the matcher configuration these messages are forwarded
to the remote communication component (2). It is the responsibility of
this component to upload the message to its remote peer component
(3). Since we use a data channel of a cellular phone network, the
remote communication component only uploads the buffered data in
certain configurable time intervals.

>>>>

\begin{table}[!htb]
\caption{\label{tab:RS232_Config}RS232 Serial Port Configuration}
\centering
\begin{tabular}{l l}
\hline
Baud Rate&9600\\
Data Bit&8\\
Parity&None\\
Handshake&None\\
\hline
\end{tabular}
\end{table}

@@

After producing the SondeDataContainer data, the YSI Sonde component will wrap
it up in a DSP Message Message and pass it to the DSP Broker for its delivery.
However, our use case scenario is that the message must go from the local
sensor device to the server. For this reason, we have developed a pair of
client and server DSP components specialized in transferring and receiving 
serialized objects throught the communication channel using the HTTP protocol
\cite{RFC2068}.

\begin{itemize}
  \item DSP Wire Transport Client: takes a collection of DSP messages and
  transmit them using an HTTP client API written in JAVA \cite{http-client}. As
  a non-functional requirement, a DSP administrator can set the interval in
  which this component will transmit messages to other components;
  \item DSP Wire Transport Server: is implemented using the Java Servlets
  technology \cite{java-servlets}, and is used to receive the collection of DSP
  messages transmitted, and potentially send DSP messages back to the sensor
  station. 
\end{itemize}

One of the non-functional requirements for the DSP is to maximize the
utilization of the communication channel. For this specific reason, we opted to
add the type Messages Container, which contains a collection of DSP messages,
and specific identifiers of the hosting sensor. Figure
\ref{FIG_DSP_MSGS_CONTAINER} contains the structure of the DSP Messages
Container.

\begin{figure}[!htb]
\centering
\epsfig{file=dsp-messages-container, width=8cm}
\caption{\label{FIG_DSP_MSGS_CONTAINER} The structure of Messages Container.}
\end{figure}

Some remarks regarding the Messages Container and it's implementation are as
follows:

\begin{itemize}
  \item Container with or without Messages Container: an instance of
  MessagesContainer may or may not have DSP messages;
  \item Container may be used to acknowledge messages using a similar strategy
  as the Slide Windowing protocol \cite{slide-window}. 
\end{itemize}

\subsection{Sending Messages Container}

It's important to note that, at this point, the DSP Broker had already checked
with the Matcher which are the DSP components that will be receive a copy of
the message in question. The matcher had specific instructions to use the DSP
Wire Transport Client component as the default ``Proxy'' or default gateway, if
you prefer.

By building a MessagesContainer instance, the Wire Transport Client adds all
the messages addressed to the ``destinationHost'', with specific UUID of
the component (2).

\subsection{Receiving Messages Container}

After the DSP server receives the message, it directly delivers to the
local DSP Broker all the messages contained in the Messages Container server.
In addition to that, the Messages Container might also include an attribute
called acknowledgeUntil, which determines the next actions that will occur in
the system.
